\documentclass[letterpaper, 12pt]{extarticle}

\usepackage[scale=.79]{geometry}

\linespread{2}

\usepackage{STYs/common}%.sty
\usepackage{STYs/ADDMC}%.sty
\usepackage{STYs/docs}%.sty

% \rfoot{Page \thepage{} of \pageref{LastPage}}

\usepackage[bookmarksnumbered,hidelinks]{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% \textbf{Latest version}: \vpHomepage \\ This version:
% 2019/11/12

\begin{center}
  \textbf{STATEMENT OF RESEARCH} \\
  \vp
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

I started my Ph.D. program in Computer Science at Rice University in 2017.
I expect to finish my Master's degree by December 2019 and my Ph.D. degree by May 2022.
The general theme of my research interests is artificial intelligence.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Past Research: Logic Programming}

During 2015-2016, under the supervision of Dr. Nelson Rushton at Texas Tech University, I participated in a NASA-funded project.
He designed the logic programming language \llang{} to encode NASA safety-critical procedures.
I implemented \llang{} by automating its translation into \aplong{} (another logic programming language whose solver was already built) \cite{b_aprolog}.

During 2016-2018, guided by Dr. Michael Gelfond at Texas Tech University, I investigated \cplong, a more expressive logic programming language \cite{b_crprolog}.
In particular, a \cp{} program is said to have antichain property if none of its answer set is a proper subset of another.
The problem was to find syntactic conditions which guarantee this semantically desirable property.
One such condition was found: the program's dependency graph being acyclic and having no directed path from one cr-rule-head-vertex to another \cite{phan2018syntactic}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Current Research: Boolean Model Counting}

In 2017, I started working with Dr. Moshe Vardi and Jeffrey Dudek at Rice University.
We study Boolean model counting, a fundamental \#P-complete problem \cite{valiant79}.
We developed an algorithm to solve the model counting problem more efficiently using algebraic decision diagrams \cite{BFGHMPS97}, dynamic programming \cite{howard66}, and early projection \cite{MPPV04}.
I implemented the algorithm to produce \addmc, a new tool for model counting.
I compared \addmc{} to four existing state-of-the-art model counters: \cachet{} \cite{SBBK04}, \ctd{} \cite{darwiche2004new}, \minictd{} \cite{OD15}, and \df{} \cite{lagniez2017improved}.
\addmc{} was shown to be competitive \cite{addmcAaai}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Future Research: Related Counting Problems}

I plan to evaluate two potential improvements to \addmc, our model counting tool.
First, \addmc{} can benefit from additional efficient data structures, including affine algebraic decision diagrams \cite{sanner2005affine} and AND/OR multi-valued decision diagrams \cite{mateescu2008and}.
Second, the heuristics \addmc{} uses may be improved with tree-decomposition techniques, which have been shown to make the \#P-hard problem of tensor-network contraction more tractable \cite{dudek2019efficient}.
Another future research direction is to assess \addmc-like frameworks (efficient data structure, dynamic programming, and early projection) on problems related to model counting such as Bayesian inference \cite{pearl1985bayesian}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{apalike}
\bibliography{BIBs/ADDMC,BIBs/crprolog}%.bib

\end{document}
